---
title: "ERA5 Hourly Data (Nepal)"
author: "Shirish Maharjan"
date: "2023-10-03"
output: html_document
---

# Load libraries 
```{r}
library(dplyr)
library(data.table)
library(readxl)
```

# Load Max, Min Temp and Total precp datasets 
```{r}
tempMax_1950_1979 <- fread("E:/GIIS/ERA5 Hourly Data/Data/Orignal Data (First)/tempMax_1950_1979.csv")
tempMax_1980_2022 <- fread("E:/GIIS/ERA5 Hourly Data/Data/Orignal Data (First)/tempMax_1980_2022.csv")

tempMin_1950_1979 <- fread("E:/GIIS/ERA5 Hourly Data/Data/Orignal Data (First)/tempMin_1950_1979.csv")
tempMin_1980_2022 <- fread("E:/GIIS/ERA5 Hourly Data/Data/Orignal Data (First)/tempMin_1980_2022.csv")

precTot_1950_1979 <- fread("E:/GIIS/ERA5 Hourly Data/Data/Orignal Data (First)/precTot_1950_1979.csv")
precTot_1980_2022 <- fread("E:/GIIS/ERA5 Hourly Data/Data/Orignal Data (First)/precTot_1980_2022.csv")

```

#Merging two different date datasets into one (1950-2022)
```{r}
tempMax_1950_2022 <- rbind(tempMax_1950_1979, tempMax_1980_2022) %>% 
  dplyr::select(-V1)

tempMin_1950_2022 <- rbind(tempMin_1950_1979, tempMin_1980_2022) %>% 
  dplyr::select(-V1)

precTot_1950_2022 <- rbind(precTot_1950_1979, precTot_1980_2022) %>% 
  dplyr::select(-V1)

full_date <- tempMax_1950_2022 %>% 
  select(year, month, day)

```

# Change Kelvin to degree celcius and metre to millimetre 

```{r}
tempMax_1950_2022 <- tempMax_1950_2022 %>% 
   select(-year, -month, -day) %>% 
   mutate_all(~ . - 273.15)

tempMin_1950_2022 <- tempMin_1950_2022 %>% 
   select(-year, -month, -day) %>% 
   mutate_all(~ . - 273.15)

precTot_1950_2022 <- precTot_1950_2022 %>% 
   select(-year, -month, -day) %>% 
  mutate_all(~ . * 1000)


```


# Binding Date and formatted Temp (Degree Celclius) and Precp Data (Millimeter) 

```{r}
tempMax_1950_2022 <- cbind(full_date, tempMax_1950_2022)
tempMin_1950_2022 <- cbind(full_date, tempMin_1950_2022)
precTot_1950_2022 <- cbind(full_date, precTot_1950_2022)
```


# Write final data 
```{r}
write.csv(tempMax_1950_2022, "E:/GIIS/ERA5 Hourly Data/Data/Formatted Data SM (Second)/tempMax_1950_2022.csv")
write.csv(tempMin_1950_2022, "E:/GIIS/ERA5 Hourly Data/Data/Formatted Data SM (Second)/tempMin_1950_2022.csv")
write.csv(precTot_1950_2022, "E:/GIIS/ERA5 Hourly Data/Data/Formatted Data SM (Second)/precTot_1950_2022.csv")

```


# PHASE 2
# Spatial join between grid/points and local units to find out which palika containts which grid/points
# We take average of those grids. If municipality A has 2-3 grids/then we take average of it. 

```{r}
tempMax_1950_2022 <- fread("E:/GIIS/ERA5 Hourly Data/Data/Formatted Data SM (Second)/tempMax_1950_2022.csv")
tempMin_1950_2022 <- fread("E:/GIIS/ERA5 Hourly Data/Data/Formatted Data SM (Second)/tempMin_1950_2022.csv")
precTot_1950_2022 <- fread("E:/GIIS/ERA5 Hourly Data/Data/Formatted Data SM (Second)/precTot_1950_2022.csv")

grid_palika_join <- read_excel("E:/GIIS/ERA5 Hourly Data/Data/Grid_Palika_Join(Third)/Gird_Palika_join.xlsx")

```

#Remove unwanted columns from dataframes 

```{r}
tempMax_1950_2022 <- tempMax_1950_2022 %>% 
  select(-V1)

tempMin_1950_2022 <- tempMin_1950_2022 %>% 
  select(-V1)

precTot_1950_2022 <- precTot_1950_2022 %>% 
  select(-V1)

grid_palika_join <- grid_palika_join %>% 
  select(DISTRICT, Province,GaPa_NaPa, unique_id)


```


# Transpose the data and Left join according to the "unique_id" in both dataframes

# tempMax

```{r}
#Transpose the data so that it is easier to leftjoin

tempMax_1950_2022_transpose <- tempMax_1950_2022 %>% 
  t() %>% 
  as.data.frame() %>% 
  slice(-(1:3))

# Make a new column name "unique_id" so that two dataframes have common column name

tempMax_1950_2022_transpose <- tempMax_1950_2022_transpose %>% 
  mutate(unique_id = row.names(tempMax_1950_2022_transpose))

# Change unique_id class to numeric

tempMax_1950_2022_transpose$unique_id <- as.numeric(tempMax_1950_2022_transpose$unique_id)

# left join grid_palika_join "unique_id" with tempMax_1950_2022_transpose "unique_id"

tempMax_1950_2022_join <- grid_palika_join %>%
  left_join(tempMax_1950_2022_transpose, by = c("unique_id" = "unique_id")) 

# Actual (Working)

# Join using Municipality only 

tempMax_1950_2022_municipality <- tempMax_1950_2022_join %>%
  group_by(GaPa_NaPa) %>%
  summarize(across(everything(), mean)) %>% 
  t() %>% 
  as.data.frame()

# Join using District only 

tempMax_1950_2022_district <- tempMax_1950_2022_join %>%
  group_by(DISTRICT) %>%
  summarize(across(everything(), mean)) %>% 
  t() %>% 
  as.data.frame()


# Join using Province only 

tempMax_1950_2022_Province <- tempMax_1950_2022_join %>%
  group_by(Province) %>%
  summarize(across(everything(), mean)) %>% 
  t() %>% 
  as.data.frame()

# Remove unwanted row names from data frames 

tempMax_1950_2022_municipality <- tempMax_1950_2022_municipality %>% 
  slice(-2,-3,-4)

tempMax_1950_2022_district <- tempMax_1950_2022_district %>% 
  slice(-2,-3,-4)

tempMax_1950_2022_Province <- tempMax_1950_2022_Province%>% 
  slice(-2,-3,-4)

# Make Municipality names as row names 

colnames(tempMax_1950_2022_municipality) <- tempMax_1950_2022_municipality %>% 
  slice(1)

tempMax_1950_2022_municipality <- tempMax_1950_2022_municipality %>% 
  slice(-1)

# Make district names as row names 

colnames(tempMax_1950_2022_district) <- tempMax_1950_2022_district %>% 
  slice(1)

tempMax_1950_2022_district <- tempMax_1950_2022_district %>% 
  slice(-1)

# Make Municipality names as row names 

colnames(tempMax_1950_2022_Province) <- tempMax_1950_2022_Province %>% 
  slice(1)

tempMax_1950_2022_Province <- tempMax_1950_2022_Province %>% 
  slice(-1)

```

# Add year, month and date column in newly made dataframe (municipality, district and province wise)

```{r}
date <- tempMax_1950_2022 %>% 
  select(year, month, day)

tempMax_1950_2022_municipality <- cbind(date, tempMax_1950_2022_municipality)
tempMax_1950_2022_district <- cbind(date, tempMax_1950_2022_district)
tempMax_1950_2022_Province <- cbind(date, tempMax_1950_2022_Province)

```

# Write tempMax datasets 

```{r}
write.csv(tempMax_1950_2022_municipality, "E:/GIIS/ERA5 Hourly Data/Data/Average_grid_data (Fourth)/Municipality/tempMax_1950_2022_municipality.csv", row.names = FALSE)
write.csv(tempMax_1950_2022_district, "E:/GIIS/ERA5 Hourly Data/Data/Average_grid_data (Fourth)/District/tempMax_1950_2022_district.csv", row.names = FALSE)
write.csv(tempMax_1950_2022_Province, "E:/GIIS/ERA5 Hourly Data/Data/Average_grid_data (Fourth)/Province/tempMax_1950_2022_province.csv", row.names = FALSE)

```








# tempMin

```{r}
#Transpose the data so that it is easier to leftjoin

tempMin_1950_2022_transpose <- tempMin_1950_2022 %>% 
  t() %>% 
  as.data.frame() %>% 
  slice(-(1:3))

# Make a new column name "unique_id" so that two dataframes have common column name

tempMin_1950_2022_transpose <- tempMin_1950_2022_transpose %>% 
  mutate(unique_id = row.names(tempMin_1950_2022_transpose))

# Change unique_id class to numeric

tempMin_1950_2022_transpose$unique_id <- as.numeric(tempMin_1950_2022_transpose$unique_id)

# left join grid_palika_join "unique_id" with tempMin_1950_2022_transpose "unique_id"

tempMin_1950_2022_join <- grid_palika_join %>%
  left_join(tempMin_1950_2022_transpose, by = c("unique_id" = "unique_id")) 

# Actual (Working)

# Join using Municipality only 

tempMin_1950_2022_municipality <- tempMin_1950_2022_join %>%
  group_by(GaPa_NaPa) %>%
  summarize(across(everything(), mean)) %>% 
  t() %>% 
  as.data.frame()

# Join using District only 

tempMin_1950_2022_district <- tempMin_1950_2022_join %>%
  group_by(DISTRICT) %>%
  summarize(across(everything(), mean)) %>% 
  t() %>% 
  as.data.frame()


# Join using Province only 

tempMin_1950_2022_Province <- tempMin_1950_2022_join %>%
  group_by(Province) %>%
  summarize(across(everything(), mean)) %>% 
  t() %>% 
  as.data.frame()

# Remove unwanted row names from data frames 

tempMin_1950_2022_municipality <- tempMin_1950_2022_municipality %>% 
  slice(-2)

tempMin_1950_2022_district <- tempMin_1950_2022_district %>% 
  slice(-2,-3,-4)

tempMin_1950_2022_Province <- tempMin_1950_2022_Province%>% 
  slice(-2,-3,-4)

# Make Municipality names as row names 

colnames(tempMin_1950_2022_municipality) <- tempMin_1950_2022_municipality %>% 
  slice(1)

tempMin_1950_2022_municipality <- tempMin_1950_2022_municipality %>% 
  slice(-1)

# Make district names as row names 

colnames(tempMin_1950_2022_district) <- tempMin_1950_2022_district %>% 
  slice(1)

tempMin_1950_2022_district <- tempMin_1950_2022_district %>% 
  slice(-1)

# Make Municipality names as row names 

colnames(tempMin_1950_2022_Province) <- tempMin_1950_2022_Province %>% 
  slice(1)

tempMin_1950_2022_Province <- tempMin_1950_2022_Province %>% 
  slice(-1)

```

# Add year, month and date column in newly made dataframe (municipality, district and province wise)

```{r}
date <- tempMin_1950_2022 %>% 
  select(year, month, day)

tempMin_1950_2022_municipality <- cbind(date, tempMin_1950_2022_municipality)
tempMin_1950_2022_district <- cbind(date, tempMin_1950_2022_district)
tempMin_1950_2022_Province <- cbind(date, tempMin_1950_2022_Province)

```

# Write tempMin datasets 

```{r}
write.csv(tempMin_1950_2022_municipality, "E:/GIIS/ERA5 Hourly Data/Data/Average_grid_data (Fourth)/Municipality/tempMin_1950_2022_municipality.csv", row.names = FALSE)
write.csv(tempMin_1950_2022_district, "E:/GIIS/ERA5 Hourly Data/Data/Average_grid_data (Fourth)/District/tempMin_1950_2022_district.csv", row.names = FALSE)
write.csv(tempMin_1950_2022_Province, "E:/GIIS/ERA5 Hourly Data/Data/Average_grid_data (Fourth)/Province/tempMin_1950_2022_province.csv", row.names = FALSE)

```





# precTot

```{r}
#Transpose the data so that it is easier to leftjoin

precTot_1950_2022_transpose <- precTot_1950_2022 %>% 
  t() %>% 
  as.data.frame() %>% 
  slice(-(1:3))

# Make a new column name "unique_id" so that two dataframes have common column name

precTot_1950_2022_transpose <- precTot_1950_2022_transpose %>% 
  mutate(unique_id = row.names(precTot_1950_2022_transpose))

# Change unique_id class to numeric

precTot_1950_2022_transpose$unique_id <- as.numeric(precTot_1950_2022_transpose$unique_id)

# left join grid_palika_join "unique_id" with precTot_1950_2022_transpose "unique_id"

precTot_1950_2022_join <- grid_palika_join %>%
  left_join(precTot_1950_2022_transpose, by = c("unique_id" = "unique_id")) 

# Actual (Working)

# Join using Municipality only 

precTot_1950_2022_municipality <- precTot_1950_2022_join %>%
  group_by(GaPa_NaPa) %>%
  summarize(across(everything(), mean)) %>% 
  t() %>% 
  as.data.frame()

# Join using District only 

precTot_1950_2022_district <- precTot_1950_2022_join %>%
  group_by(DISTRICT) %>%
  summarize(across(everything(), mean)) %>% 
  t() %>% 
  as.data.frame()


# Join using Province only 

precTot_1950_2022_Province <- precTot_1950_2022_join %>%
  group_by(Province) %>%
  summarize(across(everything(), mean)) %>% 
  t() %>% 
  as.data.frame()

# Remove unwanted row names from data frames 

precTot_1950_2022_municipality <- precTot_1950_2022_municipality %>% 
  slice(-2)

precTot_1950_2022_district <- precTot_1950_2022_district %>% 
  slice(-2,-3,-4)

precTot_1950_2022_Province <- precTot_1950_2022_Province%>% 
  slice(-2,-3,-4)

# Make Municipality names as row names 

colnames(precTot_1950_2022_municipality) <- precTot_1950_2022_municipality %>% 
  slice(1)

precTot_1950_2022_municipality <- precTot_1950_2022_municipality %>% 
  slice(-1)

# Make district names as row names 

colnames(precTot_1950_2022_district) <- precTot_1950_2022_district %>% 
  slice(1)

precTot_1950_2022_district <- precTot_1950_2022_district %>% 
  slice(-1)

# Make province names as row names 

colnames(precTot_1950_2022_Province) <- precTot_1950_2022_Province %>% 
  slice(1)

precTot_1950_2022_Province <- precTot_1950_2022_Province %>% 
  slice(-1)

```

# Add year, month and date column in newly made dataframe (municipality, district and province wise)

```{r}
date <- precTot_1950_2022 %>% 
  select(year, month, day)

precTot_1950_2022_municipality <- cbind(date, precTot_1950_2022_municipality)
precTot_1950_2022_district <- cbind(date, precTot_1950_2022_district)
precTot_1950_2022_Province <- cbind(date, precTot_1950_2022_Province)

```

# Write precTot datasets 

```{r}
write.csv(precTot_1950_2022_municipality, "E:/GIIS/ERA5 Hourly Data/Data/Average_grid_data (Fourth)/Municipality/precTot_1950_2022_municipality.csv", row.names = FALSE)
write.csv(precTot_1950_2022_district, "E:/GIIS/ERA5 Hourly Data/Data/Average_grid_data (Fourth)/District/precTot_1950_2022_district.csv", row.names = FALSE)
write.csv(precTot_1950_2022_Province, "E:/GIIS/ERA5 Hourly Data/Data/Average_grid_data (Fourth)/Province/precTot_1950_2022_province.csv", row.names = FALSE)

```





